\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.

### 2016-10-17 ms.tex
examples

@@

\begin{Verbatim}[frame=single]
> spider_params.plot\_system()
\end{Verbatim}

will generate a plot like figure \ref{fig:plot_system}

>>>>

\textsc{spiderman} comes prepackaged with several plotting scripts to make visualisation of the model simple.

@@

\begin{Verbatim}[frame=single]
> spider_params.plot_planet()
\end{Verbatim}

Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date.

\begin{Verbatim}[frame=single]
> spider_params.plot_system()
\end{Verbatim}

will generate a plot like figure \ref{fig:plot_system}, which is a scale diagram of the system. The desired phase or julian date can be given as an argument. These plots can be very useful for visualising the physical impacts of
